### 2024-06-07 Scripts/Scripts-collection.Rmd
Update Scripts-collection.Rmd

@@

```{r Fig s4e}

@@

df_recombinations_all <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\acinetobacter-recombinations-consensus_blocks_all.csv)')
df_pi <- read.table(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\all_patients-acinetobacter.pi)",header = T)

@@

df_acinetobacter <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\all_patients-snps_distribution-acinetobacter-region1.csv)')
df_acinetobacter_filtered <- subset(df_acinetobacter,PatientID %in% my_order)

df_tree <- read.tree(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\draft_only-outgroup_removed-snpscalling_filtered_resolved.tre)")
df_tree2 <- read.tree(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\draft_only-outgroup_removed-snpscalling_filtered_resolved.tre2)")
df_meta <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\metadata-filename2sampleid.csv)")

tree_order_sampleid <- c('P105','P124','P114','P156','P141','P132','P151','P118','P130','P113','P143',
                         'P123','P144','P112','P136','P77','P25','P52','P146','P23','P26','P157')
df_acinetobacter_filtered2 <- subset(df_acinetobacter,PatientID %in% tree_order_sampleid)

@@

```{r Fig s5a}
df_top_abundant_mges <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\mobile_elements_finder-contigs_all-most_abundant_mges.csv)')

>>>>

```
### Figure S4
### --------------------------------------------------------------------------------------------------------------------------------------------

@@

### Figure 5
### --------------------------------------------------------------------------------------------------------------------------------------------

@@

df_recombinations_all <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\acinetobacter-recombinations-consensus_blocks_all.csv)') # save in the same file 'acinetobacter-recombination.txt'
df_pi <- read.table(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\all_patients-acinetobacter.pi)",header = T) # save in the same file 'acinetobacter-recombination.txt'

@@

df_acinetobacter <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\all_patients-snps_distribution-acinetobacter-region1.csv)')
df_acinetobacter_filtered <- subset(df_acinetobacter,PatientID %in% my_order)
df_tree2 <- read.tree(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\draft_only-snpscalling_filtered_resolved.tre)")
tree_order_sampleid <- c('P105','P124','P114','P156','P141','P132','P151','P118','P130','P113','P143',
                         'P123','P144','P112','P136','P77','P25','P52','P146','P23','P26','P157')
df_acinetobacter_filtered2 <- subset(df_acinetobacter,PatientID %in% tree_order_sampleid)

@@

### Figure S5
### --------------------------------------------------------------------------------------------------------------------------------------------

```{r Fig s5a}

df_top_abundant_mges <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\mobile_elements_finder-contigs_all-most_abundant_mges.csv)')
